Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-08-23 paper/main.tex
feature importance tables

\begin{table}[]
\begin{tabular}{llc}
Name & Category & Gini Importance \\ \bottomrule
Size-P & Contextual (Syntactic)               & 0.112 \\
Stmt-Constr-C3= & Contextual (Syntactic)      & 0.061 \\
Expr-Constr-P=List & Contextual (Syntactic)   & 0.055 \\
PythonBlame & Dynamic (Error location)        & 0.039 \\
Type=unknown & Dynamic (Type)                 & 0.037 \\
Type-P=unknown & Contextual (Type)            & 0.037 \\
PythonMsg=IndexError & Dynamic (Error message)& 0.033 \\
Size & Syntactic                              & 0.028 \\
Expr-Constr-P=Dictionary & Contextual (Syntactic) & 0.027 \\
Size-C1 & Contextual (Syntactic)              & 0.024 \\
Expr-Constr=Var & Syntactic                   & 0.020 \\
Type-C1=unknown & Contextual (Type)           & 0.020 \\
\toprule
\end{tabular}
\caption{Feature predictive power (for a Top-3 Decision Tree
learned on the entire dataset).}
\label{tab-feature-predictive-power}
\end{table}

\begin{table}[]
\begin{center}
\begin{tabular}{llc}
Name & Category & F-score \\ \bottomrule
Stmt-Constr-C3= & Contextual (Syntactic) & 69 \\
Size & Syntactic                         & 63 \\
PythonBlame & Dynamic (Error location)   & 50 \\
Type-P=LIST & Contextual (Type)          & 36 \\
Type-C1=bool & Contextual (Type)         & 30 \\
Type-P=unknown & Contextual (Type)       & 28 \\
Type-C1= & Contextual (Type)             & 25 \\
Size-C3 & Contextual (Syntactic)         & 20 \\
Op-Constr-C1= & Contextual (Syntactic)   & 20 \\
Size-C1 & Contextual (Syntactic)         & 18 \\
Type-P=DICT & Contextual (Type)          & 17 \\
Type=str & Dynamic (Type)                & 12 \\
\toprule
\end{tabular}
\end{center}
\caption{Feature predictive power as measured by ANOVA.  The F-score in
shown in
thousands to two significant figures; all p-values are less than 0.01.}
\label{tab-anova}
\end{table}

>>>>

\begin{table}[]
\begin{tabular}{llc}
Name                      & Category                & Gini Importance \\ \bottomrule
P size                    & Contextual (Syntactic)  & 0.112 \\
C3 is statement           & Contextual (Syntactic)  & 0.061 \\
P is list literal         & Contextual (Syntactic)  & 0.055 \\
Program crashes here      & Dynamic (Error location)& 0.039 \\
Type is unknown           & Dynamic (Type)          & 0.037 \\
P type is unknown         & Contextual (Type)       & 0.037 \\
Err message is IndexError & Dynamic (Error message) & 0.033 \\
Size                      & Syntactic               & 0.028 \\
P is dictionary literal   & Contextual (Syntactic)  & 0.027 \\
C1 size                   & Contextual (Syntactic)  & 0.024 \\
Is variable               & Syntactic               & 0.020 \\
C1 type is unknown        & Contextual (Type)       & 0.020 \\
\toprule
\end{tabular}
\caption{Feature predictive power (for a Top-3 Decision Tree
learned on the entire dataset). P and C1-C3 refer to the parent and
first three children of the node in question.}
\label{tab-feature-predictive-power}
\end{table}

\begin{table}[]
\begin{center}
\begin{tabular}{llc}
Name                     & Category                & F-score \\ \bottomrule
C3 is statement          & Contextual (Syntactic)  & 69 \\
Size                     & Syntactic               & 63 \\
Program crashes here     & Dynamic (Error location)& 50 \\
P type is list           & Contextual (Type)       & 36 \\
C1 type is bool          & Contextual (Type)       & 30 \\
P type is unknown        & Contextual (Type)       & 28 \\
C1 is expression         & Contextual (Type)       & 25 \\
C3 size                  & Contextual (Syntactic)  & 20 \\
C1 is binary or unary op & Contextual (Syntactic)  & 20 \\
C1 size                  & Contextual (Syntactic)  & 18 \\
P type is dictionary     & Contextual (Type)       & 17 \\
Type is string           & Dynamic (Type)          & 12 \\
\toprule
\end{tabular}
\end{center}
\caption{Feature predictive power as measured by ANOVA.  The F-score in
shown in
thousands to two significant figures; all p-values are less than 0.01.}
\label{tab-anova}
\end{table}
